Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-21 xrb2/paper.tex
Added enuc and temperature maximum plot

\newcommand{\avg}[1]{\overline{#1}}
\newcommand{\avgtwod}[1]{\langle~#1 \rangle}
\newcommand{\rms}[2]{\left(\delta#1\right)_{r_{#2}}}
\newcommand{\mymax}[1]{\left(#1\right)_{\rm max}}

@@

@@

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each 
	simulation. {\color{blue}$v_0$} is the flame velocity {\color{blue}in the $+r$ direction} at $t 
	= 0~\mathrm{ms}$. The initial flame 
	velocities and accelerations are derived from a quadratic least-squares fit to each of the 
	datasets for times $t \gtrsim 20~\mathrm{ms}$. {\color{blue} Using these fit parameters we calculate the velocity at $t = 50~\mathrm{ms}$, $v_{50}$, at which point the flames have reached steady propagation.}}
	\tablehead{\colhead{run} & \colhead{$v_0$ (km s$^{-1}$)} & \colhead{$a$ (km s$^{-2}$)} & \colhead{$v_{50}$ (km s$^{-1}$)}} 
	\startdata
  {\tt F1000}     & $(3.414 \pm 0.008)$ & $(-1.03 \pm 0.13)$ & $(3.36 \pm 0.01)$\\
  {\tt F500}      & $(3.077 \pm 0.013)$ & $(5.41 \pm 0.19)$ & $(3.35 \pm 0.02)$\\
  {\tt F500\_2E8} & $(3.760 \pm 0.015)$ & $(1.74 \pm 0.25)$ & $(3.85 \pm 0.02)$\\
  {\tt F500\_3E8} & $(-5.293 \pm 0.100)$ & $(357.41 \pm 2.15)$ & $(12.58 \pm 0.15)$\\
	\enddata
	%
\end{deluxetable}

@@

Figure~\ref{fig:flame_speeds_1} gives the position of the flame front as a function of time for the $\tt{F500}$ and $\tt{F1000}$ runs 
(blue and orange, respectively) to show the dependence on rotation rate. {\color{blue}In 
\citet{flame_wave1}, we 
applied a linear least-squares fit to the flame front position as a function of time to estimate the propagation velocity. 
For this study we instead fit a quadratic curve to each set of data, as some of the hotter $500~\mathrm{Hz}$ 
runs exhibit significant acceleration. We discarded the data points with $t \lesssim 20~\mathrm{ms}$, 
since these correspond to the initial transient period before the flame has begun to propagate 
steadily.} The fit parameters yield estimates of the flame acceleration and velocity at $t = 0~\mathrm{ms}$, 
which are provided in Table~\ref{table:flame_speeds}. {\color{blue}Note that the listed velocity is 
only 
a parameter that may be used to calculate the flame speed at an arbitrary time. It is not an 
estimate of the true initial velocity of the flame, since the flame has not achieved ignition yet 
at $t = 0~\mathrm{ms}$. We use the fit parameters to calculate the flame speeds at $t = 50~\mathrm{ms}$ (when the flame has reached steady propagation), given in the fourth column of Table \ref{table:flame_speeds}.} \MarginPar{KE: Outside of updating the data in the table, is there anything else we 
want to add to this para?}

We found in \citet{flame_wave1} that the flame speed, $s$, obeys the following relation:
\begin{equation}
	\label{eqn:flame_speed_scaling}
	s \appropto L_R (\enucdot)^{\half} \propto \frac{(\enucdot)^{\half}}{\Omega},
\end{equation}
where $\enucdot$ is the specific nuclear energy generation rate and $L_R$ is the Rossby length 
described by Equation \ref{eqn:rossby}. This finding was consistent with the results of 
\citet{cavecchi:2013}, who noted that the flame speeds in their simulations scaled with the Rossby 
length. As seen in Figure~\ref{fig:flame_speeds_1}, there is no obvious inverse scaling of the 
flame speed with rotation rate in this set of runs. We observed earlier, however, that nuclear 
reactions progress more quickly at higher rotation rate. This results in a higher $\enucdot$ --- up 
to four to six times higher near the burning front after the flame ignites --- which may counteract 
the reduction in flame speed from the increased Coriolis confinement. We also observe that 
$\tt{F500}$ accelerates faster than $\tt{F1000}$, which appears to experience a small deceleration 
at early times. This disparity may be a direct result of the difference in Coriolis force.

@@

@@

\begin{figure}[t]
\centering
\plotone{compare_500Hz_abar}
\caption{\label{fig:compare_500Hz_abar} Comparison of $\bar{A}$ for 3 different $500~\mathrm{Hz}$ models with neutron star temperatures $T_{\rm star}$ of $10^8~\mathrm{K}$, $2\times10^8~\mathrm{K}$ and $3\times10^8~\mathrm{K}$ ($\tt{F500}$, $\tt{F500\_2e8}$, and $\tt{F500\_3e8}$, respectively), and resulting envelope structures.  Each flame is shown at $70~\mathrm{ms}$.} 
\end{figure}

Figure~\ref{fig:compare_500Hz_abar} shows $\bar{A}$ for three $500~\mathrm{Hz}$ simulations with different initial temperature structures at $t = 70~\mathrm{ms}$. The hottest of the three plotted models, $\tt{F500\_3E8}$, has a faster propagating flame (this will be discussed further in Section \ref{ssec:temp_prop}). {\color{blue} It also reaches slightly higher $\bar{A}$ values than the two cooler runs. We do not plot $\tt{F500\_4E8}$ here because it fails to form a clear burning front. The Figure~\ref{fig:abar_hot} $\bar{A}$-$T$ phase plots of $\tt{F500}$ (left) and $\tt{F500\_3E8}$ (middle) also reflect these $\bar{A}$ features, with $\tt{F500\_3E8}$ reaching slightly higher $\bar{A}$ values. $\tt{F500\_3E8}$ also reaches higher $\enucdot$ values at the low end of the temperature range ($< 0.5 \times 10^9 \mathrm{K}$). There appear to be more causally connected regions across a range of $\bar{A}$ at low temperatures for $\tt{F500\_3E8}$ than for $\tt{F500}$, suggesting that the higher $\enucdot$ for $\tt{F500\_3E8}$ generates burning in certain reaction pathways that are not present in the cooler $\tt{F500}$ run.}
\MarginPar{relate this section back to Kiran's max temperature and $\enucdot$ plots once they're added, note that $\tt{F500\_3E8}$ doesn't reach as high temperatures, less evolved abar than $\tt{F1000}$}

In contrast to the models with $T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$, $\tt{F500\_4E8}$ is so hot that the organized flame structure is lost. The fuel layer undergoes stable burning and essentially simmers in place, rather than forming a flame. This process has been observed in neutron stars with accretion rates that exceed the Eddington limit \citep{fujimoto1981,bildsten1998thermonuclear,keek2009effect}; in this model we have essentially recreated the conditions found in such stars with high accretion rates. This model burns so strongly that it is only run out to $40~\mathrm{ms}$. After an initial period when the burning moves across the domain, residual burning continues and eventually ignites the entire fuel layer at late times, as shown in Figures \ref{fig:4e8_stacked_enuc} and \ref{fig:4e8_stacked_abar} for three snapshots taken in the last ten seconds of the simulation. In Figure~\ref{fig:4e8_stacked_enuc}, $\enucdot$ reaches values of $10^{18} - 10^{20}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ across the domain and at heights up to $\sim 0.5\times 10^4~\mathrm{cm}$. There is still significant burning occurring even higher, with $\enucdot$ reaching $\sim 10^{15}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ at heights up to $\sim 0.8\times 10^4~\mathrm{cm}$. For comparison, the next hottest run ($\tt{F500\_3E8}$) only reaches maximum $\enucdot$ values on the order of $10^{18}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ {\color{blue} (see Figure ?? Kiran $\enucdot$ plot)}, even at the latest timesteps ($\sim 70~\mathrm{ms}$, when the flame is most developed). {\color{blue} Significant $\enucdot$ values for all other runs are confined to the flame front, rather than spanning the entire domain}.

Figure~\ref{fig:4e8_stacked_abar} shows $\bar{A}$ for $\tt{F500\_4E8}$. Again, burning extends across the domain and high into the atmosphere and fuel layer, lacking the characteristic flame structure shown in $\bar{A}$ plots for the lower temperature $500~\mathrm{Hz}$ runs (see Figure~\ref{fig:compare_500Hz_abar}). A distinct mass of material appears to have broken out of the atmosphere near the axis of symmetry. The atmosphere edge is located at $\sim 1.2\times 10^4~\mathrm{cm}$. {\color{blue}A similar effect is also visible (to a lesser extent) in the $\tt{F500\_3E8}$ plot in Figure \ref{fig:compare_500Hz_abar}, with a faint haze of material rising above the flame. However, this is likely to be a numerical artefact rather than a true physical effect, and a result of the boundary conditions imposed at the axis of symmetry for these simulations.} $\tt{F500\_4E8}$ clearly reaches much higher $\bar{A}$ values across the domain (especially at the latest snapshot, $t = 40~\mathrm{ms}$) compared to all the other runs described in this paper (see Figures \ref{fig:compare_500Hz_abar}, \ref{fig:time_series_500}, and \ref{fig:time_series_1000}). This is not surprising, since as we have shown in our simulations with differing initial temperature structures, the burning is very temperature-sensitive. \MarginPar{is it generally temperature-sensitive, or only sensitive to the highest temperatures?}

 {\color{blue} Though $\tt{F500\_4E8}$ does not form a distinct burning front, it does achieve greatly enhanced burning, as shown in the Figure~\ref{fig:abar_hot} $\bar{A}$-$T$ phase plot (right panel). Not only is $\tt{F500\_4E8}$ significantly hotter overall compared to all other runs}, but there is a large causally connected region across a wide range of $\bar{A}$. This indicates that the hotter temperature has facilitated significant burning in reaction pathways that were not favored at the lower temperatures. The reaction pathways are also very disrupted for $\tt{F500\_4E8}$ compared to the cooler runs, suggesting that the hotter temperature leads to more vigorous mixing. {\color{blue}Indeed, this appears to be the case looking at Figure~\ref{fig:4e8_stacked_abar} and the right panel of Figure~\ref{fig:uv_hot} (discussed further in section~\ref{ssec:temp_prop}). The disrupted reaction pathways resemble those found in Figure \ref{fig:abar} for the highest rotation $\tt{F1000}$ run, though they are even more dramatically disrupted for $\tt{F500\_4E8}$. $\tt{F500\_4E8}$ is also noticably hotter than $\tt{F1000}$, even though it is run for significantly less time ($t = 40~\mathrm{ms}$ vs $t = 100~\mathrm{ms}$). While the correlation between increased temperature, greater mixing, and enhanced burning seen in $\tt{F500\_4E8}$ agrees with our previous anaylses, without an increased rotation and Coriolis force the $\tt{F500\_4E8}$ run seems insufficiently confined to maintain a burning front.} \MarginPar{is this interpretation of the lack of Coriolis force correct?}

@@

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three $500~\mathrm{Hz}$ runs with
		$T_{\rm star}$ of $10^8~\mathrm{K}$, $2\times10^8~\mathrm{K}$ and $3\times10^8~\mathrm{K}$ ($\tt{F500}$, $\tt{F500\_2e8}$, and $\tt{F500\_3e8}$, respectively). The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$. Note that due to its rapid acceleration, $\tt{F500\_3E8}$ 
		(green) is only run out to $\sim 70~\mathrm{ms}$ to avoid surpassing the domain boundary.}
\end{figure}

The $u$-$\rho$ phase plot in Figure~\ref{fig:urho_hot} shows that the horizontal velocity for the $T_{\rm star} = 4\times10^8$~K is significantly greater in magnitude than for the two cooler runs. The $u$-$v$ plot in Figure~\ref{fig:uv_hot} further demonstrates this, as again we see that the magnitude of the velocity in the 
vertical direction of the flame for the hottest run is also significantly larger. This motion therefore most likely corresponds to the vortical motion rather than to the propagation of the flame itself, something which is further supported by the fact that the velocity magnitude is two to three orders of magnitude greater than the flame speeds listed in Table~\ref{table:flame_speeds}. Also of interest in these plots is that the coolest run does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs at this time ($40~\mathrm{ms}$). As can be seen in Figure~\ref{fig:uv} (which was plotted at $100~\mathrm{ms}$), this does develop more at later times. Similar to what saw when comparing the runs with different rotation rates, it would therefore appear that it takes longer for the flame to develop when $T_{\rm star}$ is cooler.

\begin{figure}[t]
    \centering
    \plotone{urho_plot_hotter}
    \caption{\label{fig:urho_hot}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the $500~\mathrm{Hz}$ runs with $T_{\rm star}$ of $10^8~\mathrm{K}$, $3\times10^8~\mathrm{K}$ and $4\times10^8~\mathrm{K}$ ($\tt{F500}$, $\tt{F500\_3e8}$, and $\tt{F500\_4e8}$) at $t = 40~\mathrm{ms}$ {\color{blue} (the latest time that $\tt{F500\_4E8}$ is run out to). The run with $T_{\rm star} = 2\times10^8~\mathrm{K}$ ($\tt{F500\_2E8}$) closely resembles the cooler $\tt{F500}$ run, and is not shown here}.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_hotter}
    \caption{\label{fig:uv_hot}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the $500~\mathrm{Hz}$ runs with $T_{\rm star}$ of $10^8~\mathrm{K}$, $3\times10^8~\mathrm{K}$ and $4\times10^8~\mathrm{K}$ ($\tt{F500}$, $\tt{F500\_3e8}$, and $\tt{F500\_4e8}$) at $t = 40~\mathrm{ms}$. {\color{blue} The run with $T_{\rm star} = 2\times10^8~\mathrm{K}$ ($\tt{F500\_2E8}$) closely resembles the cooler $\tt{F500}$ run, and is not shown here}.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{abar_plot_hotter}
    \caption{\label{fig:abar_hot}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the $500~\mathrm{Hz}$ runs with $T_{\rm star}$ of $10^8~\mathrm{K}$, $3\times10^8~\mathrm{K}$ and $4\times10^8~\mathrm{K}$ ($\tt{F500}$, $\tt{F500\_3e8}$, and $\tt{F500\_4e8}$) at $t = 40~\mathrm{ms}$. {\color{blue} The run with $T_{\rm star} = 2\times10^8~\mathrm{K}$ ($\tt{F500\_2E8}$) closely resembles the cooler $\tt{F500}$ run, and is not shown here}.}
\end{figure}

>>>>

\newcommand{\avg}[1]{\overline{#1}}
\newcommand{\avgtwod}[1]{\langle~#1 \rangle}
\newcommand{\repavg}[1]{\langle \langle #1 \rangle \rangle}
\newcommand{\rms}[2]{\left(\delta#1\right)_{r_{#2}}}
\newcommand{\mymax}[1]{\left(#1\right)_{\rm max}}

@@

\begin{figure}
	\plotone{maxima_vs_time.pdf}
	\caption{\label{fig:maxima}Estimates of temperature (left panel) and nuclear energy generation 
	rate (right panel) in the burning region as functions of time. The quantities on the vertical 
	axes are the averages defined by Equation \ref{eqn:top_percentile_avg}.}
\end{figure}

{\color{blue}
For some of our analysis, we would like to have a means of estimating the temperature and nuclear 
energy generation rate in the burning region of each simulation. For this purpose, we define 
$\repavg{Q}$ to be the mass weighted average
\begin{equation}
	\label{eqn:top_percentile_avg}
	\repavg{Q} \equiv \frac{\sum_{c_i} m(c_i) Q(c_i)}{\sum_{c_i} m(c_i)}; ~c_i \in C_{99}(Q).
\end{equation}
\noindent Here, $C_{99}(Q)$ is the set of grid cells with $Q$ values in the top percentile, and 
$Q(c_i)$ is the value of the quantity $Q$ in cell $c_i$. An alternative to doing this averaging is 
to simply take the maximum of the quantity across the entire simulation domain, but using 
$\repavg{Q}$ instead allows us to track changes over a region rather than at a single localized 
point. Figure \ref{fig:maxima} shows $\repavg{T}$ and $\repavg{\enucdot}$ as functions of time for 
the subset of our runs that achieve a propagating flame. This figure is referenced at several 
points throughout the subsequent sections.
}

@@

\MarginPar{Mike wants to check vertical profiles of atmosphere behind flame}

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each 
	simulation. $v_0$ is the flame velocity in the $+r$ direction at $t 
	= 0~\mathrm{ms}$. The initial flame 
	velocities and accelerations are derived from a quadratic least-squares fit to each of the 
	datasets for times $t \gtrsim 20~\mathrm{ms}$. Using these fit parameters we calculate the 
	velocity at $t = 50~\mathrm{ms}$, $v_{50}$, at which point the flames have reached steady 
	propagation.}
	\tablehead{\colhead{run} & \colhead{$v_0$ (km s$^{-1}$)} & \colhead{$a$ (km s$^{-2}$)} & 
	\colhead{$v_{50}$ (km s$^{-1}$)}} 
	\startdata
  {\tt F1000}     & $3.414 \pm 0.008$ & $-1.03 \pm 0.13$ & $3.362 \pm 0.010$\\
  {\tt F500}      & $3.077 \pm 0.013$ & $5.41 \pm 0.19$ & $3.347 \pm 0.016$\\
  {\tt F500\_2E8} & $3.760 \pm 0.015$ & $1.74 \pm 0.25$ & $3.847 \pm 0.020$\\
  {\tt F500\_3E8} & $-5.293 \pm 0.100$ & $357 \pm 2$ & $12.58 \pm 0.15$\\
	\enddata
	%
\end{deluxetable}

@@

Figure~\ref{fig:flame_speeds_1} gives the radial position of the flame front as a function of time 
for the $\tt{F500}$ and $\tt{F1000}$ runs (blue and orange, respectively) to show the dependence on 
rotation rate. In \citet{flame_wave1}, we applied a linear least-squares fit to the flame front 
position as a function of time to estimate the propagation velocity. As some of the flames in this 
set of simulation runs exhibit significant acceleration, for this study we instead fit the data 
with a quadratic curve of the form:
\begin{equation}
	\label{eqn:quadratic_fit}
	\color{blue} r(t) = \half a t^2 + v_0 t + r_0
\end{equation}
\noindent The parameter $a$ is the acceleration of the flame, $v_0$ is the velocity at $t = 
0~\mathrm{ms}$, and $r_0$ is the position at $t = 0~\mathrm{ms}$. We do not include the data points 
with $t \lesssim 20~\mathrm{ms}$ when performing the fit, since these correspond to the initial 
transient period before the flame has begun to propagate steadily. The values of $a$ and $v_0$ for 
the full suite of simulation runs are provided in Table~\ref{table:flame_speeds}. Note that $v_0$ 
is only a parameter that may be used to calculate the flame speed at an arbitrary time. It is not 
an estimate of the true initial velocity of the flame, since the flame has not achieved ignition 
yet at $t = 0~\mathrm{ms}$. We use the fit parameters to calculate the flame speeds at $t = 
50~\mathrm{ms}$ (when the flame has reached steady propagation), given in the fourth column of 
Table \ref{table:flame_speeds}.

We found in \citet{flame_wave1} that the flame speed, $s$, obeys the following relation:
\begin{equation}
	\label{eqn:flame_speed_scaling}
	s \appropto L_R (\enucdot)^{\half} \propto \frac{(\enucdot)^{\half}}{\Omega},
\end{equation}
where $\enucdot$ is the specific nuclear energy generation rate and $L_R$ is the Rossby length 
described by Equation \ref{eqn:rossby}. This finding was consistent with the results of 
\citet{cavecchi:2013}, who noted that the flame speeds in their simulations scaled with the Rossby 
length. As seen in Figure~\ref{fig:flame_speeds_1}, there is no obvious inverse scaling of the 
flame speed with rotation rate in this set of runs. We observed earlier, however, that nuclear 
reactions progress more quickly at higher rotation rate. {\color{blue}This results in a higher 
$\enucdot$ --- up 
to three to four times higher near the burning front after the flame ignites (see Figure 
\ref{fig:maxima}) --- which may counteract the reduction in flame speed from the increased Coriolis 
confinement.} We also observe that $\tt{F500}$ accelerates faster than $\tt{F1000}$, which appears 
to experience a small deceleration at early times. This disparity may be a direct result of the 
difference in Coriolis force.

@@

 \MarginPar{NF: I think we should plot peak enucdot as a function of time for each run, it would be useful for me to reference it in one of the later sections}

@@

\begin{figure}[t]
\centering
\plotone{compare_500Hz_abar}
\caption{\label{fig:compare_500Hz_abar} Comparison of $\bar{A}$ for 3 different $500~\mathrm{Hz}$ models with different neutron star temperatures, $T_\mathrm{star}$, and resulting envelope structures.  Each flame is shown at $70~\mathrm{ms}$.} 
\end{figure}

Figure~\ref{fig:compare_500Hz_abar} shows $\bar{A}$ for three $500~\mathrm{Hz}$ simulations with different initial temperature structures at $t = 70~\mathrm{ms}$. The hottest of the three models, $\tt{F500\_3E8}$, has a faster propagating flame (this will be discussed further in Section \ref{ssec:temp_prop}).

Similar to the $\bar{A}$ trends found for different rotation rates in Figure \ref{fig:abar}, the $\bar{A}$-$T$ phase plot in Figure~\ref{fig:abar_hot} suggests that the actual reactions happening in the hottest run may be different than for the cooler runs. Not only is the $\tt{F500\_3E8}$ flame itself significantly hotter overall, but there is a large causally connected region across a wide range of $\bar{A}$. This indicates that the hotter temperature has facilitated significant burning in reaction pathways that were not favored at the lower temperatures. The reaction pathways are also very disrupted for $\tt{F500\_3E8}$ compared to the cooler runs, suggesting that the hotter temperature leads to more turbulent mixing. Compared to the highest rotation rate run, $\tt{F1000}$, $\tt{F500\_3E8}$ reaches a peak temperature roughly $1 \times 10^9~\mathrm{K}$ higher ($\sim 2.7 \times 10^9~\mathrm{K}$ versus $\sim 1.7 \times 10^9~\mathrm{K}$). Though increasing the rotation rate does seem to concentrate the burning and increase the peak temperature, it does not reach the same level as directly increasing the temperature at the crust.

In contrast to the models with $T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$, $\tt{F500\_4E8}$ is so hot that the organized flame structure is lost. The fuel layer undergoes stable burning and essentially simmers in place, rather than forming a flame. This process has been observed in neutron stars with accretion rates that exceed the Eddington limit \citep{fujimoto1981,bildsten1998thermonuclear,keek2009effect}; in this model with have essentially recreated the conditions found in such stars with high accretion rates. This model burns so strongly that it is only run out to $40~\mathrm{ms}$. After an initial period of burning moves across the domain, residual burning continues and eventually ignites the entire fuel layer at late times, as shown in Figures \ref{fig:4e8_stacked_enuc} and \ref{fig:4e8_stacked_abar} for three snapshots taken in the last ten seconds of the simulation. In Figure~\ref{fig:4e8_stacked_enuc}, $\enucdot$ reaches values of $10^{18} - 10^{20}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ across the domain and at heights up to $\sim 0.5\times 10^4~\mathrm{cm}$. There is still significant burning occurring even higher, with $\enucdot$ reaching $\sim 10^{15}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ at heights up to $\sim 0.8\times 10^4~\mathrm{cm}$. For comparison, the next hottest run ($\tt{F500\_3E8}$) only reaches maximum $\enucdot$ values of $10^{18}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ and a maximum height of $\sim 0.5\times 10^4~\mathrm{cm}$, even at the latest timesteps ($\sim 70~\mathrm{ms}$, when the flame is most developed). Significant $\enucdot$ values for $\tt{F500\_3E8}$ are confined to the flame front, rather than spanning the entire domain.

\MarginPar{NF: should I include a plot for this or is it ok to just say it?}
Figure~\ref{fig:4e8_stacked_abar} shows $\bar{A}$ for $\tt{F500\_4E8}$. Again, burning extends across the domain and high into the atmosphere and fuel layer, lacking the characteristic flame structure shown in $\bar{A}$ plots for the lower temperature $500~\mathrm{Hz}$ runs (see Figure~\ref{fig:compare_500Hz_abar}). A distinct mass of material appears to have broken out of the atmosphere near the axis of symmetry. The atmosphere edge is located at $\sim 1.2\times 10^4~\mathrm{cm}$. {\color{blue}A similar effect is also visible (to a lesser extent) in the $\tt{F500\_3E8}$ plot in Figure \ref{fig:compare_500Hz_abar}, with a faint haze of material rising above the flame. However, this is likely to be a numerical artefact rather than a true physical effect, and a result of the boundary conditions imposed at the axis of symmetry for these simulations.} $\tt{F500\_4E8}$ clearly reaches much higher $\bar{A}$ values across the domain (especially at the latest snapshot, $t = 40~\mathrm{ms}$) compared to all the other runs described in this paper (see Figures \ref{fig:compare_500Hz_abar}, \ref{fig:time_series_500}, and \ref{fig:time_series_1000}). This is not surprising, since as we have shown in our simulations with differing initial temperature structures, the burning is very temperature-sensitive.

@@

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three $500~\mathrm{Hz}$ runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$. Note that due to its rapid acceleration, $\tt{F500\_3E8}$ 
		(green) is only run out to $\sim 70~\mathrm{ms}$ to avoid surpassing the domain boundary.}
\end{figure}

The $u$-$\rho$ phase plot in Figure~\ref{fig:urho_hot} shows that the horizontal velocity for the $T_{\rm star} = 3\times10^8$~K is sufficiently  \MarginPar{should this say "significantly"?} greater in magnitude than for the two cooler runs. The $u$-$v$ plot in Figure~\ref{fig:uv_hot} further demonstrates this, as again we see that the magnitude of the velocity in the vertical direction of the flame for the hottest run is also significantly larger. This motion therefore most likely corresponds to the vortical motion rather than to the propagation of the flame itself, something which is further supported by the fact that the velocity magnitude is 2-3 orders of magnitude greater than the flame speeds listed in Table~\ref{table:flame_speeds}. Also of interest in these plots is that the coolest run does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs at this time ($40~\mathrm{ms}$). As can be seen in Figure~\ref{fig:uv} (which was plotted at $100~\mathrm{ms}$), this does develop more at later times. Similar to what saw when comparing the runs with different rotation rates, it would therefore appear that it takes longer for the flame to develop when $T_{\rm star}$ is cooler.

\begin{figure}[t]
    \centering
    \plotone{urho_plot_hotter}
    \caption{\label{fig:urho_hot}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the $500~\mathrm{Hz}$ runs with $T_{\rm star}$ of $10^8~\mathrm{K}$, $3\times10^8~\mathrm{K}$ and $4\times10^8~\mathrm{K}$ at $t = 40~\mathrm{ms}$.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_hotter}
    \caption{\label{fig:uv_hot}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the $500~\mathrm{Hz}$ runs with $T_{\rm star}$ of $10^8~\mathrm{K}$, $3\times10^8~\mathrm{K}$ and $4\times10^8~\mathrm{K}$ at $t = 40~\mathrm{ms}$.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{abar_plot_hotter}
    \caption{\label{fig:abar_hot}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the $500~\mathrm{Hz}$ runs with $T_{\rm star}$ of $10^8~\mathrm{K}$, $3\times10^8~\mathrm{K}$ and $4\times10^8~\mathrm{K}$ at $t = 40~\mathrm{ms}$.}
\end{figure}
